\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[a4paper, margin=.8in]{geometry}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{url}

\usepackage{enumitem}

\setlength{\textwidth}{5.1in} % Text width of the document

\renewcommand{\baselinestretch}{1.45}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Mehmet~Ali~Tu\u{g}tekin Turan} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft0.5\hoffset\centerline{Postdoctoral Research Associate, INRIA} % Your address
\moveleft0.5\hoffset\centerline{615 Rue du Jardin-Botanique, 54600 Villers-lès-Nancy, France}
\moveleft0.5\hoffset\centerline{+33 (7) 66 40 92 75}
\moveleft0.5\hoffset\centerline{tugtekin.turan@inria.fr}
\moveleft0.5\hoffset\centerline{\url{https://scholar.google.com/citations?user=w3OrQIIAAAAJ}}
%----------------------------------------------------------------------------------------

\begin{resume}

\section{RESEARCH \\ INTEREST}

Speech Signal Processing | Automatic Speech Recognition | On-Body Sensing Speech Enhancement | Wearable Computing | Machine Learning for Healthcare
\vspace{1em}

\section{WORK \\ EXPERIENCE}
{\sl \textbf{Postdoctoral Researcher}} \hfill June 2019 - Present \\[.3em]
INRIA, Multispeech Team, France, \url{https://team.inria.fr/multispeech} \vspace{.3em}
\begin{itemize}
\item Working for \textit{H2020 Comprise} project, \url{https://www.compriseh2020.eu}
\item Conducting research and development under a privacy-preserving setting
\item Developing speaker adapted acoustic and language models
\end{itemize}
\vspace{1em}

\section{EDUCATION}

{\sl \textbf{Doctor of Philosophy}} \hfill October 2013 - March, 2019 \\[.3em]
Ko\c{c} University, Electrical Engineering, Istanbul, Turkey \vspace{.3em}
\begin{itemize}
\item \textit{Thesis:} Use of Transfer Learning for Automatic Dietary Monitoring through Throat Microphone Recordings
\item \textit{Read Online:} \url{https://doi.org/10.5281/zenodo.3841956}
\item \textit{Advisor:} Dr.~Engin Erzin
\item Full scholarship from Ford Motor Company, Turkey
\item Grant support by the Scientific and Technological Research Council of Turkey (T\"{U}B{\.I}TAK)
\end{itemize}

{\sl \textbf{Master of Science}} \hfill September 2011 - August 2013 \\[.3em]
Ko\c{c} University, Electrical Engineering, Istanbul, Turkey \vspace{.3em}
\begin{itemize}
\item \textit{Thesis:} Enhancement of Throat Microphone Recordings Using Gaussian \\ Mixture Model Probabilistic Estimator
\item \textit{Read Online:} \url{https://arxiv.org/abs/1804.05937}
\item \textit{Advisor:} Dr.~Engin Erzin
\item Full scholarship from Ko\c{c} University
\end{itemize}

{\sl \textbf{Undergraduate Degree}} \hfill September 2007 - June 2011 \\[.3em]
Bilkent University, Electrical Engineering, Ankara, Turkey \vspace{.3em}
\begin{itemize}
% \item \textit{GPA:} 3.11 / 4.00
\end{itemize}

\vspace{1em}
\section{TECHNICAL \\ SKILLS}

{\sl Programming Languages:} Python, C/C++, R \\
{\sl Tools:} Kaldi, PyTorch, SRILM, Keras, HTK, Bash, MATLAB, \LaTeX, Linux \\

\vspace{-.5em}
\section{SOCIETY \\ MEMBERSHIP}

IEEE \& IEEE-SPS\hfill September 2011 - Present \\
ISCA \hfill September 2012 - Present

\vspace{1em}
\section{RELEVANT \\ COURSEWORK}

Random Processes | Big Data Processing | Digital Communications | Machine Learning | Introduction to Artificial Intelligence | Digital Signal Processing | Numerical Methods | Linear Systems Theory | Information Theory | Digital Image and Video Processing | Detection and Estimation Theory | Computer Vision and Pattern Recognition | Digital Speech and Audio Processing | Probabilistic Graphical Methods | Information Theory

\vspace{1em}
\section{TEACHING \\ ASSISTANT \\DUTIES}
Digital Systems Design with FPGAs | Probability and Statistics | Digital Speech and Audio Processing | Embedded Systems with ATMEL Assembly | Quantitative Reasoning using MS Excel | Digital Signal Processing | Random Variables and Stochastic Processes | Introduction to Programming with MATLAB

\vspace{1em}
\section{LANGUAGES}
Turkish, \textit{Native} \hspace{.1em}(\textit{Nationality}: Turkish) \\
English, \textit{Fluent} \\
French, \textit{Beginner}

\vspace{.5em}
\section{LEISURE \\ INTEREST}
Amateur Cooking | Playing Guitar | Volunteering for Animals | Motorcycle Touring | Mobile Programming

\vspace{1em}
\section{JOURNAL \\ PAPERS}

\begin{itemize}[leftmargin=*]
    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Improving Phoneme Recognition of Throat Microphone Speech Recordings Using Transfer Learning." \textit{under revision in} Elsevier Speech Communication, 2020.

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Domain Adaptation for Food Intake Classification with Teacher/Student Learning." \textit{to appear in} IEEE Transactions on Multimedia, 2020.

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Source and Filter Estimation for Throat-Microphone Speech Enhancement." IEEE Transactions on Audio, Speech and Language Processing (TASLP), 2016. \\ \url{https://doi.org/10.1109/TASLP.2015.2499040}

    \item Can Ya\u{g}l\i, \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Artificial Bandwidth Extension of Spectral Envelope Along a Viterbi Path." Elsevier Speech Communication, 2013. \hspace{.1em}
    \url{https://doi.org/10.1016/j.specom.2012.07.003}
\end{itemize}

\vspace{1em}
\section{CONFERENCE \\ PAPERS}

\begin{itemize}[leftmargin=*]
    \item \textbf{M.~A.~Tu\u{g}tekin Turan}, Emmanuel Vincent and Denis Jouvet. "Achieving Multi-accent ASR via Unsupervised Acoustic Model Adaptation." INTERSPEECH, 2020. \hspace{.1em} \url{https://hal.inria.fr/hal-02907929/document}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Monitoring Infant's Emotional Cry in Domestic Environments Using the Capsule Network Architecture." INTERSPEECH, 2018. \hspace{.1em} \url{https://doi.org/10.21437/Interspeech.2018-2187}

    % \item \textbf{M.~A.~T.~Turan} and Engin Erzin. "Ingestion Detection Using Long Short-Term Memory Recurrent Neural Networks" \textit{submitted to} International Conference on Pervasive Computing Technologies for Healthcare, 2018

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Detection of Food Intake Events From Throat Microphone Recordings Using Convolutional Neural Networks." IEEE International Conference on Multimedia and Expo (ICME), 2018. \\ \url{https://doi.org/10.1109/ICMEW.2018.8551492}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Empirical Mode Decomposition of Throat Microphone Recordings for Intake Classification." International Workshop on Personal Health and Health Care, ACM Multimedia, 2017. \\ \url{https://doi.org/10.1145/3132635.3132640}

    \item Johannes Abel et al. "A Subjective Listening Test of Six Different Artificial Bandwidth Extension Approaches in English, Chinese, German, and Korean." IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2016. \hspace{.1em} \url{https://doi.org/10.1109/ICASSP.2016.7472812}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Synchronous Overlap and Add of Spectra for Enhancement of Excitation in Artificial Bandwidth Extension of Speech." INTERSPEECH, 2015. \\ \url{https://www.isca-speech.org/archive/interspeech_2015/i15_2588.html}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Enhancement of Throat Microphone Recordings by Learning Phone-Dependent Mappings of Speech Spectra." IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2013. \hspace{.1em} \url{https://doi.org/10.1109/ICASSP.2013.6639029}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "A New Statistical Excitation Mapping for Enhancement of Throat Microphone Recordings." INTERSPEECH, 2013. \\ \url{https://www.isca-speech.org/archive/interspeech_2013/i13_3244.html} \\
\end{itemize}

\section{IEEE \\ REGIONAL \\ CONFERENCE \\ PAPERS}

\begin{itemize}[leftmargin=*]
    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Food Intake Detection Using Autoencoder Based Deep Neural Networks." IEEE Signal Processing and Communications Applications Conference (SIU), 2018. \\ \url{https://doi.org/10.1109/SIU.2018.8404522}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Classification of Ingestion Sounds Using Hilbert-Huang Transform." IEEE Signal Processing and Communications Applications Conference (SIU), 2017. \\ \url{https://doi.org/10.1109/SIU.2017.7960505}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Food Intake Classification Using Throat Microphone." IEEE Signal Processing and Communications Applications Conference (SIU), 2016. \url{https://doi.org/10.1109/SIU.2016.7496129}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "Artificial Bandwidth Extension of Speech Excitation." IEEE Signal Processing and Communications Applications Conference (SIU), 2015. \url{https://doi.org/10.1109/SIU.2015.7130085}

    \item \textbf{M.~A.~Tu\u{g}tekin Turan} and Engin Erzin. "A Phonetic Classification for Throat Microphone Enhancement." IEEE Signal Processing and Communications Applications Conference (SIU), 2014. \\ \url{https://doi.org/10.1109/SIU.2014.6830559}
\end{itemize}

\end{resume}
\end{document}
